High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-28 notebooks/mnist.qmd
mnist benchmark

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="MNIST",
    n_individuals=100,
    initialization=:identity,
)

@@

```{julia}
@chain bmk() begin
    @group_by(dataname, generator, model, variable)
    @summarize(mean=mean(value),sd=std(value))
    @ungroup
    @filter(variable == "distance_from_targets")
end
```

>>>>

bmk = benchmark(
    counterfactual_data; 
    models=model_dict, 
    generators=generator_dict, 
    measure=measures,
    suppress_training=true, dataname="MNIST",
    n_individuals=5,
    factual=0, target=1,
    initialization=:identity,
)

@@

```{julia}
@chain bmk() begin
    @group_by(dataname, generator, model, variable)
    @summarize(mean=mean(value),sd=std(value))
    @ungroup
    @filter(variable == "distance_from_energy")
end
```
